A highly-available move operation for replicated trees

### 2019-06-17 paper/move-op.tex
paper: integration with OOPSLA framework

\subsection{Commutativity of apply\_op}

@@

@@

>>>>

\subsection{Convergence}

@@

\subsubsection{Commutativity of apply\_op}

@@

\subsubsection{Strong eventual consistency}

Gomes et al.~\cite{Gomes:2017gy} define a framework in Isabelle/HOL for proving the strong eventual consistency properties of CRDTs.
Based on the commutativity proof above we integrate our tree datatype with this framework, and thus prove that our move operation on trees does indeed guarantee strong eventual consistency.
The details of this proof are given in the open source Isabelle source files.\footnote{\url{https://github.com/trvedata/move-op}}
